### 2017-04-06 paper/evaluation.tex
minor tweaks with Luis

%\begin{figure}[t!]
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \footnotesize
    \centering
    \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
%    }
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
    %\end{figure}
\end{wrapfigure}      
Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
where parallelism is enabled by default.  Column ``\emph{Subject}''
indicates the name of the project, column ``\emph{\# of modules}''
indicates the number of detected modules containing tests, and column
``\emph{Mode}'' shows the parallel configuration mode used in those
modules (see Section~\ref{sec:modes}).  It came as a surprise the
observation that no project used distinct configurations in their
modules. Considering our set of \numMedLong{} projects, we found that
only \textbf{\numProjectsPar{}} of those projects had parallelism
enabled by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.  
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}

>>>>

%\begin{figure}[t!]
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \footnotesize
    \centering
    \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
%    }
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
    %\end{figure}
\end{wrapfigure}      
Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
where parallelism is enabled by default in Maven.  Column
``\emph{Subject}'' indicates the name of the project, column
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.  We note that, considering these projects, the
modules that do not use the configuration cited use the sequential
configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
use sequential configuration.

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering
our set of \numMedLong{} projects, we found that only
\textbf{\numProjectsPar{}} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
